---
title: "Simulation 04272021"
author: "Firman M. Firmansyah"
date: "March 11, 2021"
output:
  pdf_document: default
  html_document: default
---

# INTRODUCTION

This simulation aims to explain the micromechanism leading to amplified segregated friendship on Facebook.
While the paper focuses on ethnicity, the results might be applicable for other social identities.

Manuscript:

Firmansyah, F. M. (2021). How does Facebook retain segregated friendship? An agent-based model approach. ArXiv:2109.08862 [Cs]. http://arxiv.org/abs/2109.08862


## Required Library

```{r, echo=FALSE, message=FALSE, warning=FALSE}

packages <- c("tidyverse", "igraph", "ggpubr", "summarytools")

# Install packages not yet installed
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Packages loading
invisible(lapply(packages, library, character.only = TRUE))

options(dplyr.summarise.inform = FALSE)

```

## Functions
### Agent Population

This function generates a population with the following parameters. 

Input:
 n       = number of agents
 si      = number of social identity
 w_si    = weight for each social identity
 p_mino  = parameter for minority for each social identity; Bernoulli distribution with regard to w_si
 p_to    = parameter for tie outreachability; binomial distribution with trial equal to max of possible value of w_si
 p_tc    = parameter for tie capacity
    m_tc = mean, normal distribution
    d_tc = standard deviation, normal distribution

Output:
 dataframe with
  SI = social identity 1 through n
  TO = tie outreachability
  TC = tie capacity
  AG = agent

```{r}

agents <- function(n=100, si=2, w_si=c(1,2), p_mino=c(.5, .5), p_to=.5, p_tc=c(m_tc=3, sd_tc=1)) {
  if(length(p_mino)<si){
    p_mino = rep(p_mino,si) #by default p_mino are the same for all social identities
  }
  if(length(w_si)<si){
    w_si = rep(w_si,si)#by default w_si are the same for all social identity weights
  }
  population <- matrix(NA, nrow=n, ncol=si)
  for (i in 1:si){
    population[,i] <- w_si[i]*rbinom(n, 1, p_mino[i]) #generating weighted social identity
  }
  population <- as.data.frame(population)
  colnames(population) <- paste0("SI", 1:si)
  population$TO <- rbinom(nrow(population), sum(w_si[1:si]), p_to) #generating tie outreachability
  population$TC <- abs(round(rnorm(nrow(population), p_tc[[1]], p_tc[[2]]),0)) #generating tie capacity
  population$AG <- 1:n #generating agent's names
  return(population)
}

```



### Friendship Development

This function takes input from agent population then generates dyadic friendships.
It always reaches an equlibrium, in which, given the tie outreachabiity and tie capacity parameters, no additional friendship can be further made.

Input:
 dataset from agents

Output:
 dataframe with 
  $friends_yes = developed friendship
    AG1, AG2        = agents in the dyads
    DIST            = social identity distance, calculated using Manhattan distance
    AG1_TO, AG2_TO  = agents' tie outreachability
  $friends_no  = undeveloped friendship
    AG1, AG2        = agents in the dyads
    DIST            = social identity distance, calculated using Manhattan distance
    AG1_TO, AG2_TO  = agents' tie outreachability
    WHY_NOT         = reason why two agents can be friends
          0         = one or both agents can only generate zero-length of ties
          99        = one or both agents have reached their maximum tie capacity
    
This the improved version, which is faster from the previous version.

```{r}

friendships <- function(data=must_from_agents) {
  
potential_friends <- t(combn(1:nrow(data), 2)) #all possible friendships
random_potential_friends <- potential_friends[sample(nrow(potential_friends)),] #randomized order of potential friends


#### filter based on tie outreachability ####

distance_friends <- as.matrix(dist(data[,1:(ncol(data)-3)], upper=T, diag=T, method="manhattan")) #social identity distance
random_potential_friends <- cbind(random_potential_friends,
                                  sapply(1:nrow(random_potential_friends), function(i) distance_friends[random_potential_friends[i,][1], random_potential_friends[i,][2]]) #assign social identity disstance to dyads
)

random_potential_friends <- cbind(random_potential_friends,
                                  sapply(random_potential_friends[,1], function(i) data$TO[data$AG==i]) #assign TO for agent1
)
random_potential_friends <- cbind(random_potential_friends,
                                  sapply(random_potential_friends[,2], function(i) data$TO[data$AG==i]) #assign TO for agent2
)

random_potential_friends <- cbind(random_potential_friends,
                            sapply(1:nrow(random_potential_friends), 
                                   function(i) ifelse(random_potential_friends[i,][3] <= min(random_potential_friends[i,][4], random_potential_friends[i,][5]), 
                                                      1, 0)) #1: yes reciprocated, 0: no reciprocated
)

random_potential_friends_reciprocated <- random_potential_friends[random_potential_friends[,6] == 1,] #filter only those reciprocated

#### matrix for friends yes and friends no####

potential_friends_filtered <- random_potential_friends_reciprocated[,1:5]
friends_yes <- matrix(NA, nrow(potential_friends_filtered), 5)
friends_no <- matrix(NA, nrow(potential_friends_filtered), 5)


#### filter based on tie capacity ####

for(i in 1:nrow(potential_friends_filtered)){ 
  if (
    isTRUE(length(which(friends_yes[,1:2] == potential_friends_filtered[i,][1])) < data$TC[potential_friends_filtered[i,][1]])
    &
    isTRUE(length(which(friends_yes[,1:2] == potential_friends_filtered[i,][2])) < data$TC[potential_friends_filtered[i,][2]])
  ) { friends_yes[i,] <- potential_friends_filtered[i,] } 
  else {
    friends_no[i,] <- potential_friends_filtered[i,]
  }
}


#### why not friends

random_potential_friends_unreciprocated <- random_potential_friends[random_potential_friends[,6] == 0,]
random_potential_friends_unavailable <- cbind(friends_no, rep(99,nrow(friends_no)))
friends_no <- rbind(random_potential_friends_unreciprocated, random_potential_friends_unavailable) 

#### results ####

friends_yes <- as.data.frame(na.omit(friends_yes))
colnames(friends_yes) <- c("AG1", "AG2", "DIST", "AG1_TO", "AG2_TO")
friends_no <- as.data.frame(na.omit(friends_no))
colnames(friends_no) <- c("AG1", "AG2", "DIST", "AG1_TO", "AG2_TO", "WHY_NOT")
friends <- list("friends_yes" = friends_yes, "friends_no" = friends_no)
  
  
return(friends)

}

```


### Ego-Alter Similarity

This functions calculate how many alters (friends) share similarity with the ego.

```{r}

how_many_percent_similar_alters <- function(data1=must_from_agents, data2=must_from_friendships) {
  data2=data2$friends_yes
  
  data3 <- as_tibble(data1) %>%
    select(AG) #create a tibble with agents
  
  data3$TOTFRIE <- sapply(1:nrow(data3), function(i) length(data2$DIST[data2$AG1 == data1$AG[i] | data2$AG2 == data1$AG[i]])) #total friends 
  data3$SIMALTS <- sapply(1:nrow(data3), function(i) length(which(data2$DIST[data2$AG1 == data1$AG[i] | data2$AG2 == data1$AG[i]] == 0))) #same race 

  data3$PERCSIMALTS <- data3$SIMALTS/data3$TOTFRIE*100
  
  #data1 <- data1[,c(5,3,6)] #only for agents (AG), tie outreachability (TO), and friendship diversity index (FDI)
  
  mean_PERCSIMALTS <- mean(data3$PERCSIMALTS, na.rm = T)
  sd_PERCSIMALTS <- sd(data3$PERCSIMALTS, na.rm = T)
  
  percent_similar_alters <- list("data" = data3, "mean_percent_similar_alters" = mean_PERCSIMALTS, "sd_percent_similar_alters" = sd_PERCSIMALTS)
  
  return(percent_similar_alters)
}

```

### Agent Satisfaction

This function calculate how many agents can have friends at least eqaul to the threshold.

```{r}

who_satisfied <- function(data1=must_from_agents, data2=must_from_friendships, threshold=.5) {
  data2=data2$friends_yes
  
  data1$ALTS <- sapply(1:nrow(data1), function(i) length(which(data2[,1:2] == data1$AG[i])) )
  data1$SATISFIED <- sapply(1:nrow(data1), function(i) ifelse (data1$ALTS[i] >= threshold*data1$TC[i], "satisfied", "unsatisfied") )
  
  data1 <- data1[,(ncol(data1)-3):ncol(data1)]
  data1 <- (data1[,c(1,3,4,2)])
  
  summ_ <- table(data1$SATISFIED)
  perc_ <- round(summ_/sum(summ_)*100,2)
  
  unsatisfied_ag <- data1[which(data1$SATISFIED == "unsatisfied"), ]
  
  satisfied <- list("data" = data1, "summary" = summ_, "percentage" = perc_, "unsatisfied_agents" = unsatisfied_ag)
  
  return(satisfied)
}

```

### Social Network Viz

This function visualizes networks.

```{r}

viz_networks <- function(data1=must_from_agents, data2=must_from_friendships, color1 = "white", color2 = "black", bordercolor1 = "black", bordercolor2 = "white", legend = c("yes", "no"), bottom_text="", left_text = "", insert_title = "coba") 
  {
  
  edges <- data2$friends_yes[,1:3]
  nodes <-data1[,c(ncol(data1),1:(ncol(data1)-3))]
  gg <- graph_from_data_frame(d=edges, vertices=nodes, directed=FALSE)
  

    V(gg)[V(gg)$SI1 == 0]$color <- color1
    V(gg)[V(gg)$SI1 != 0]$color <- color2
    
    V(gg)[V(gg)$SI1 == 0]$vertex.frame.color <- bordercolor1
    V(gg)[V(gg)$SI1 != 0]$vertex.frame.color <- bordercolor2
    
    par(mar=c(2,2,2,0)) #bottom, left, top, right
    plotnya <- plot(gg, vertex.label = NA, vertex.size=17, edge.width=2.7, vertex.shapes="circle", main = insert_title)
    mtext(bottom_text, side=1, cex=.75)
    mtext(left_text, side=2, cex=.75)
    
    if (isTRUE(legend == "yes")) {
      legend(x=.9, y=.9, legend=c("majority", "minority"), pch=21, pt.bg=c(color1, color2), cex=.7, pt.cex=1.2, title=expression('Social Identity'))
    }
    else {
     
    }
    
  
  return(plotnya)
  
}

```

# SIMULATION

Simulation Design

Constant
- Social identity (si) = 1
- Minority proportion (p_mino) = .22

Manipulated Variables
- Agents (n) = 30 (offline), 300 (online)
- Tie Outreachability (p_to) = .2 (low), .5 (medium), .8 (high)
- Tie Capacity (p_tc) = (3, .25) [offline], (30, .25) [online]

Friendship process 
- process = random

Trials
- 100 for each cells = 6 x 100 = 600

## Generating Agent Populations 

```{r}

start_time <- Sys.time()
set.seed(08212021)

#manipulated variables
tie_outreachability = c(.2, .5, .8)
tie_capacity_mean = c(3, 30) #sd c(.25, .25)

#numbers of trial
trial <- 1:100

#generating table simulation
agent_population <- as_tibble(expand.grid(trial, tie_outreachability, tie_capacity_mean))
colnames(agent_population) <- c("TRIAL", "TIEOUT", "TIECAP")

## population
agent_population$ID <- 1:nrow(agent_population) #unique ID for each simulation
agent_population$POPULATION <- NA

#generating population for offline population
for (i in 1:300) {  #this is only for offline population
  agent_population$POPULATION[i] <- list(tibble(
    agents(n = 30, #n offline population 
           si = 1,
           p_mino = .22,
           p_to = agent_population$TIEOUT[i],
           p_tc = c(m_tc = agent_population$TIECAP[i], sd_tc = .25)))
  )
}

#generating population for online population
for (i in 301:600) {  #this is only for offline population
  agent_population$POPULATION[i] <- list(tibble(
    agents(n = 300, #n online population
           si = 1,
           p_mino = .22,
           p_to = agent_population$TIEOUT[i],
           p_tc = c(m_tc = agent_population$TIECAP[i], sd_tc = .25)))
  )
}

saveRDS(agent_population, "agent_population_08212021.rds")

end_time <- Sys.time()
end_time-start_time

```


## Simulating Friendship Development

```{r}

start_time <- Sys.time()
set.seed(08212021)

agent_friendship <- tibble(ID=agent_population$ID, FRIENDSHIP =NA)

#for offline and online context
for (i in 1:nrow(agent_population)) {
  agent_friendship$FRIENDSHIP[i] <- list(tibble(results = friendships(as.data.frame(agent_population$POPULATION[i]))))
}

saveRDS(agent_friendship, "agent_friendship_08212021.rds")

end_time <- Sys.time()
end_time-start_time

```
Time difference of 1.988802 hours

## Dataset

### load from simulation

```{r}

agent_population <- read_rds('agent_population_08212021.rds')
agent_friendship <- read_rds('agent_friendship_08212021.rds')

```


# GENERATED POPULATION

Unnest Population Dataset

```{r}

all_agent_populations <- agent_population %>% unnest(POPULATION)

```

## Social Identity

### tab

long table complete observations

```{r}

#all_agent_populations$SI <- paste(all_agent_populations$SI1, ifelse(all_agent_populations$SI2 == 2, 1, 0), sep="")

all_agent_populations %>%
  group_by(TIEOUT, TIECAP) %>%
  freq(SI1, report.nas = F)

#long table
social_identity_long_table <- all_agent_populations %>%
  group_by(TRIAL, TIEOUT, TIECAP, SI1) %>%
  count(SI1) %>%
  group_by (TIEOUT, TIECAP) %>%
  mutate(PERCENTAGE = n/sum(n))

```

summary table for SI count

```{r}

#short table count
social_identity_short_table_count <- all_agent_populations %>%
  group_by(TIEOUT, TIECAP, TRIAL, SI1) %>%
  count(SI1) %>%
  pivot_wider(names_from = SI1, values_from = n) %>%
  group_by(TIEOUT, TIECAP) %>%
  summarize(MEAN_MAJOR = round(mean(`0`),2), SD_MAJOR = round(sd(`0`),2), 
            MEAN_MINOR = round(mean(`1`),2), SD_MINOR = round(sd(`1`),2))

social_identity_short_table_count
  
```

summary table for SI percent 

```{r}

#short table percent
social_identity_short_table_percent <- all_agent_populations %>%
  group_by(TIEOUT, TIECAP, TRIAL, SI1) %>%
  count(SI1) %>%
  group_by (TIEOUT, TIECAP) %>%
  mutate(PERCENTAGE = n/sum(n)*10000) %>%
  pivot_wider(names_from = SI1, values_from = PERCENTAGE) %>%
  group_by(TIEOUT, TIECAP) %>%
  summarize(MEAN_MAJOR = round(mean(`0`, na.rm = T  ),1), SD_MAJOR = round(sd(`0`, na.rm = T),1), 
            MEAN_MINOR = round(mean(`1`, na.rm = T),1), SD_MINOR = round(sd(`1`, na.rm = T),1))

social_identity_short_table_percent 

```

### viz

count

```{r}

# New facet label names for TO parameters
p_to_labs <- c("TO, q = .2", "TO, q = .5", "TO, q = .8")
names(p_to_labs) <- c(.2, .5, .8)

# New facet label names for TC parameters for SI displays
p_tc_labs <- c("TC, \u03BC = 3, \u03C3\U00B2 = .25 (n = 30)", "TC, \u03BC = 30, \u03C3\U00B2 = .25 (n = 300)") #unicodes for mu and sigma square, no new line \n
names(p_tc_labs) <- c(3, 30)

si_plot_count30 <- social_identity_long_table %>%
  filter(TIECAP==3)%>%
  ggplot(aes(x=TRIAL, y=n, fill=as_factor(SI1))) +
  geom_area() + facet_grid(TIEOUT~TIECAP, scales = "free_y",
                            labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) + 
  labs(title = "Generated Social Identity", 
    x = element_blank(), y = "Count (agents)") + 
  scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) +
  scale_fill_manual(name="", #"Ethnicity", 
                  labels = c("majority", "minority"), 
                    values = c("#ED8E7C", "#A03C78")) +
  theme(plot.title = element_text(hjust = 0.5), 
        legend.position = "top")

si_plot_count300 <- social_identity_long_table %>%
  filter(TIECAP==30)%>%
  ggplot(aes(x=TRIAL, y=n, fill=as_factor(SI1))) +
  geom_area() + facet_grid(TIEOUT~TIECAP, scales = "free_y",
                            labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) + 
  labs(title = "Generated Social Identity", 
    x = element_blank(), y = "Count (agents)") + 
  scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) +
  scale_fill_manual(name="", #"Ethnicity", 
                  labels = c("majority", "minority"), 
                    values = c("#ED8E7C", "#A03C78")) +
  theme(plot.title = element_text(hjust = 0.5), 
        legend.position = "top")

social_identity_count_combined <- ggarrange(si_plot_count30 +labs(title=element_blank()) + theme(strip.text.y=element_blank()),
                                                 si_plot_count300+labs(title=element_blank(), y=element_blank()), nrow=1, common.legend = T)
social_identity_count_combined <- annotate_figure(social_identity_count_combined, top = text_grob("Social Identity", size=14  ),
                                                  bottom = text_grob("-th Simulation")) # , face = "bold"

social_identity_count_combined

```


## Tie Outreachability 

### tab

long table complete observations

```{r}

all_agent_populations %>%
  group_by(TIEOUT, TIECAP) %>%
  freq(TO, report.nas = F)

#long table
tie_outreachability_long_table <- all_agent_populations %>%
  group_by(TRIAL, TIEOUT, TIECAP) %>%
  count(TO) %>%
  group_by (TIEOUT, TIECAP) %>%
  mutate(PERCENTAGE = n/sum(n))

```

summary table for TO count

```{r}

#short table
tie_outreacability_short_table_count <- all_agent_populations %>%
  group_by(TIEOUT, TIECAP, TRIAL, TO) %>%
  count(TO) %>%
  pivot_wider(names_from = TO, values_from = n) %>%
  group_by(TIEOUT, TIECAP) %>%
  summarize(MEAN_TO_0 = round(mean(`0`),2), SD_0 = round(sd(`0`),2), 
            MEAN_TO_1 = round(mean(`1`, na.rm=T),2), SD_1 = round(sd(`1`, na.rm=T),2), 
            )

tie_outreacability_short_table_count

```

summary table for TO percent

```{r}

#short table

tie_outreacability_short_table_percent <- tie_outreachability_long_table %>%
  group_by(TIEOUT, TIECAP, TO) %>%
  summarize(MEAN_PERCENT_TO = round(mean(PERCENTAGE)*10000,2),
            SD_PERCENT_TO = round(sd(PERCENTAGE)*10000,2)) %>%
  pivot_wider(names_from = TO, values_from = c(MEAN_PERCENT_TO, SD_PERCENT_TO))

tie_outreacability_short_table_percent

```

### viz

count

```{r}

to_plot_count30 <- tie_outreachability_long_table %>%
  filter(TIECAP == 3) %>%
  mutate(TO = as.character(TO)) %>%
  ggplot(aes(x=TRIAL, y=n, fill=TO)) +
  geom_area() + facet_grid(TIEOUT ~ TIECAP,
                           labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) + 
  labs(title = "Generated Tie Outreachability", 
       x = element_blank(), y = "Count (agents)") + 
  scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) +
  scale_fill_manual(name="", #"Tie Outreachability:", 
                    labels = c("0", "1"), values = c("#C36839", "#86340A")) + 
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "top")


to_plot_count300 <- tie_outreachability_long_table %>%
  filter(TIECAP == 30)%>%
  mutate(TO = as.character(TO)) %>%
  ggplot(aes(x=TRIAL, y=n, fill=TO)) +
  geom_area() + facet_grid(TIEOUT ~ TIECAP,
                           labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) + 
  labs(title = "Generated Tie Outreachability", 
       x = element_blank(), y = "Count (agents)") + 
  scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) +
  scale_fill_manual(name="", #"Tie Outreachability:", 
                    labels = c("0", "1"), values = c("#C36839", "#86340A")) + 
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "top")


to_plot_combined <- ggarrange(to_plot_count30 +labs(title=element_blank()) + theme(strip.text.y=element_blank()),
                                                to_plot_count300+labs(title=element_blank(), y=element_blank()), 
                              nrow=1, common.legend = T)
to_plot_combined <- annotate_figure(to_plot_combined, top = text_grob("Generated Tie Outreachability", size=14),
                                    bottom = text_grob("-th Simulation"))

to_plot_combined



```

## Tie Capacity

### tab

long table

```{r}

all_agent_populations %>%
  group_by(TIEOUT, TIECAP) %>%
  freq(TC, report.nas = F)

tie_capacity_long_table <- all_agent_populations %>%
  group_by(TRIAL, TIEOUT, TIECAP) %>%
  count(TC) %>%
  group_by (TIEOUT, TIECAP) %>%
  mutate(PERCENTAGE = n/sum(n))


```

summary table for TC count

```{r}
tie_capacity_long_table %>%
  group_by(TIEOUT, TIECAP, TC) %>%
  summarize(MEAN_TC = round(mean(n),2),
            SD_TC = round(sd(n),2)) 
```

summary table for TC percent

```{r}

tie_capacity_long_table %>%
  group_by(TIEOUT, TIECAP, TC) %>%
  summarize(MEAN_PERC_TC = round(mean(PERCENTAGE)*10000,2),
            SD_PERC_TC = round(sd(PERCENTAGE)*10000,2)) 

```

### viz

count

```{r}

coba <- tie_capacity_long_table %>%
  mutate(TC = as.character(TC))

coba$TC <- factor(coba$TC, levels = as.character(c(seq(2, 4), seq(29,31)))
                  )
tc_plot_count30 <- coba %>%
  filter(TIECAP == 3) %>%
  ggplot(aes(x=TRIAL, y=n, fill=TC)) +
  geom_area() + facet_grid(TIEOUT ~ TIECAP, scales = "free_y",
                            labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) + 
  labs(title = "Generated Tie Capacity", 
    x = element_blank(), y = "Count (agents)") + 
  scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) +
 scale_fill_manual(name="", #"Tie Capacity" 
                    labels = c("2", "3", "4"), 
                   values = c("#0532a3", "#63abf7", "#0c81e8")) +
  theme(plot.title = element_text(hjust = 0.5), 
        legend.position = "top") + guides(fill = guide_legend(nrow=1))



tc_plot_count300 <- coba %>%
  filter(TIECAP == 30) %>%
  ggplot(aes(x=TRIAL, y=n, fill=TC)) +
  geom_area() + facet_grid(TIEOUT ~ TIECAP, scales = "free_y",
                            labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) + 
  labs(title = "Generated Tie Capacity", 
    x = element_blank(), y = "Count (agents)") + 
  scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) +
 scale_fill_manual(name="", #"Tie Capacity" 
                    labels = c("29", "30", "31"), 
                   values = c("#001E6C", "#5089C6", "#035397")) +
  theme(plot.title = element_text(hjust = 0.5), 
        legend.position = "top") + guides(fill = guide_legend(nrow=1))


tc_plot_combined <- ggarrange(tc_plot_count30 +labs(title=element_blank()) + theme(strip.text.y=element_blank()),
                                                tc_plot_count300+labs(title=element_blank(), y=element_blank()), nrow=1)
tc_plot_combined <- annotate_figure(tc_plot_combined, top = text_grob("Generated Tie Capacity", size=14),
                                    bottom = text_grob("-th Simulation")
                                                       )
tc_plot_combined

```

# DEVELOPED FRIENDSHIPS

## Network Visualization

### one each

one example for one scenario

```{r}

set.seed(212121)

n1 <- sample(100, 1)
n2 <- sample(101:200, 1)
n3 <- sample(201:300, 1)
n4 <- sample(301:400, 1)
n5 <- sample(401:500, 1)
n6 <- sample(501:600, 1)

par(mfrow=c(2,3))

net1 <- viz_networks(agent_population$POPULATION[[n1]], agent_friendship$FRIENDSHIP[[n1]]$results, "#ED8E7C", "#A03C78", "no", left_text = "TC, \u03BC = 3, \u03C3\U00B2 = .25", insert_title = paste0("ID = ", n1))
net2 <- viz_networks(agent_population$POPULATION[[n2]], agent_friendship$FRIENDSHIP[[n2]]$results, "#ED8E7C", "#A03C78", legend="no", insert_title = paste0("ID = ", n2))
net3 <- viz_networks(agent_population$POPULATION[[n3]], agent_friendship$FRIENDSHIP[[n3]]$results, "#ED8E7C", "#A03C78", "no", insert_title = paste0("ID = ", n3))
net4 <- viz_networks(agent_population$POPULATION[[n4]], agent_friendship$FRIENDSHIP[[n4]]$results, "#ED8E7C", "#A03C78", "no", left_text = "TC, \u03BC = 3, \u03C3\U00B2 = .25", bottom_text = "TO, q = .2", insert_title = paste0("ID = ", n4))
net5 <- viz_networks(agent_population$POPULATION[[n5]], agent_friendship$FRIENDSHIP[[n5]]$results, "#ED8E7C", "#A03C78", "no", bottom_text = "TO, q = .5", insert_title = paste0("ID = ", n5))
net6 <- viz_networks(agent_population$POPULATION[[n6]], agent_friendship$FRIENDSHIP[[n6]]$results, "#ED8E7C", "#A03C78", "no", bottom_text = "TO, q = .8", insert_title = paste0("ID = ", n6))

```

## Dyadic Friendship

### tab

count

```{r}

friend_dyad_count <- tibble(ID=agent_friendship$ID, Y0=NA, Y1=NA, N0=NA, N1=NA)
for (i in 1:nrow(friend_dyad_count)) {
  friend_dyad_count$Y0[i] <- sum(agent_friendship$FRIENDSHIP[i][[1]][[1]]$friends_yes$DIST == 0)
  friend_dyad_count$Y1[i] <- sum(agent_friendship$FRIENDSHIP[i][[1]][[1]]$friends_yes$DIST == 1)
  
  
  friend_dyad_count$N0[i] <- sum(agent_friendship$FRIENDSHIP[i][[1]][[1]]$friends_no$DIST == 0)
  friend_dyad_count$N1[i] <- sum(agent_friendship$FRIENDSHIP[i][[1]][[1]]$friends_no$DIST == 1)
}

friend_dyad_count

#summary count of developed dyads
summ_friend_dyad_count <- left_join(friend_dyad_count, agent_population[,2:4], by="ID") %>%
  group_by(TIEOUT, TIECAP) %>%
  summarize(MEAN_0_DIST = round(mean(Y0),2), SD_0_DIST = round(sd(Y0),2), MEAN_1_DIST = round(mean(Y1),2), SD_1_DIST = round(sd(Y1),2))

summ_friend_dyad_count

#saveRDS(summ_friend_dyad_count "summ_friend_dyad_count_03112021_sat.rds")
#write_csv(summ_friend_dyad_count, "summ_friend_dyad_count_03112021_sat.csv")

```

percent

```{r}

friend_dyad_percent <- tibble(ID = friend_dyad_count$ID)

#percentage of developed dyads
friend_dyad_percent$Y0PER <- friend_dyad_count$Y0/(friend_dyad_count$Y0+friend_dyad_count$Y1)*100
friend_dyad_percent$Y1PER <- friend_dyad_count$Y1/(friend_dyad_count$Y0+friend_dyad_count$Y1)*100

friend_dyad_percent

#summary percentage of developed dyads
summ_friend_dyad_percent <- left_join(friend_dyad_percent, agent_population[,2:4], by="ID") %>%
  group_by(TIEOUT, TIECAP) %>%
  summarize(MEAN_0_DIST = round(mean(Y0PER),2), SD_0_DIST = round(sd(Y0PER),2), MEAN_1_DIST = round(mean(Y1PER),2), SD_1_DIST = round(sd(Y1PER),2)) #MEYO0

summ_friend_dyad_percent

#write_csv(summ_friend_dyad_percent, "summ_friend_dyad_percent_03112021_sat.csv")

```

### viz

count viz

```{r, echo=F, warning=F}

friend_freq_df <- left_join(agent_population[,1:4], friend_dyad_count[,1:5], by="ID")

tab_friend_freq <- friend_freq_df %>%
  pivot_longer(Y0:Y1, names_to = "DYAD_DIST", values_to = "COUNT")

friendship_plot_count30 <- tab_friend_freq %>%
  filter(TIECAP == 3) %>%
  ggplot(aes(x=TRIAL, y=COUNT, fill=DYAD_DIST)) +
  geom_area() + 
  facet_grid(TIEOUT ~ TIECAP,
    labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) + 
  labs(title = "Developed Friendships", x = element_blank(), y = "Count (dyads)") + 
  scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) +
  scale_fill_manual(name="", #"Friendship:", 
                    labels = c("homogeneous", "heterogeneous"), 
                    values = c("#54436B", "#FBD400")) + 
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "top")

friendship_plot_count300 <- tab_friend_freq %>%
  filter(TIECAP == 30) %>%
  ggplot(aes(x=TRIAL, y=COUNT, fill=DYAD_DIST)) +
  geom_area() + 
  facet_grid(TIEOUT ~ TIECAP,
    labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) + 
  labs(title = "Developed Friendships", x = element_blank(), y = "Count (dyads)") + 
  scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) +
  scale_fill_manual(name="", #"Friendship:", 
                    labels = c("homogeneous", "heterogeneous"), 
                    values = c("#54436B", "#FBD400")) + 
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "top")

developed_friendship_count_combined <- ggarrange(friendship_plot_count30 +labs(title=element_blank()) + theme(strip.text.y=element_blank()),
                                                 friendship_plot_count300+labs(title=element_blank(), y=element_blank()), nrow=1, common.legend = T)
developed_friendship_count_combined <- annotate_figure(developed_friendship_count_combined, top = text_grob("Developed Dyadic Friendships", size=14),
                                                       bottom = text_grob("-th Simulation"))

developed_friendship_count_combined


```

## Ego Friendship

alter similarity

save ego alter similarity percentage dataset

ego alter similarity - majority and minority dataset

```{r}

alt_similar <- tibble(ID = agent_population$ID)
alt_similar$MEAN_SAMERACE <- sapply(1:nrow(alt_similar), function(i) how_many_percent_similar_alters(agent_population$POPULATION[[i]], agent_friendship$FRIENDSHIP[[i]]$results)$mean_percent_similar_alters)
alt_similar$SD_SAMERACE <- sapply(1:nrow(alt_similar), function(i) how_many_percent_similar_alters(agent_population$POPULATION[[i]], agent_friendship$FRIENDSHIP[[i]]$results)$sd_percent_similar_alters)
alt_similar

alt_similar_mm <- tibble(ID = agent_population$ID)

alt_similar_mm$MEAN_SAMERACE_MAJOR <- sapply(1:nrow(alt_similar_mm), function(i) how_many_percent_similar_alters(agent_population$POPULATION[[i]] %>% filter(SI1==0), agent_friendship$FRIENDSHIP[[i]]$results)$mean_percent_similar_alters)
alt_similar_mm$SD_SAMERACE_MAJOR <- sapply(1:nrow(alt_similar_mm), function(i) how_many_percent_similar_alters(agent_population$POPULATION[[i]] %>% filter(SI1==0), agent_friendship$FRIENDSHIP[[i]]$results)$sd_percent_similar_alters)

alt_similar_mm$MEAN_SAMERACE_MINOR <- sapply(1:nrow(alt_similar_mm), function(i) how_many_percent_similar_alters(agent_population$POPULATION[[i]] %>% filter(SI1!=0), agent_friendship$FRIENDSHIP[[i]]$results)$mean_percent_similar_alters)
alt_similar_mm$SD_SAMERACE_MINOR <- sapply(1:nrow(alt_similar_mm), function(i) how_many_percent_similar_alters(agent_population$POPULATION[[i]] %>% filter(SI1!=0), agent_friendship$FRIENDSHIP[[i]]$results)$sd_percent_similar_alters)


```

### tab

summary table ego alter percentage similarity

all

```{r}

summ_tab_egoaltsim_all <- left_join(agent_population[,1:4], alt_similar, by="ID") %>%
  group_by(TIEOUT, TIECAP) %>%
  summarize(MEAN_EGOALTSIM_ALL = mean(MEAN_SAMERACE), SD_EGOALTSIM_ALL = sd(SD_SAMERACE))

summ_tab_egoaltsim_all

```

majority and minority

```{r}

summ_tab_egoaltsim_majmin <- left_join(agent_population[,1:4], alt_similar_mm, by="ID") %>%
  group_by(TIEOUT, TIECAP) %>%
  summarize(MAJOR_M = mean(MEAN_SAMERACE_MAJOR), MAJOR_SD = sd(SD_SAMERACE_MAJOR,  na.rm=T),
            MINOR_M = mean(MEAN_SAMERACE_MINOR, na.rm=T), MINOR_SD = sd(SD_SAMERACE_MINOR,  na.rm=T)
            )

summ_tab_egoaltsim_majmin

```


### viz

percent

```{r, warning=F}

left_join(agent_population[,1:4], alt_similar_mm, by="ID") %>% 
  left_join(alt_similar, by="ID") %>%
  pivot_longer(c(MEAN_SAMERACE_MAJOR, MEAN_SAMERACE_MINOR, MEAN_SAMERACE), names_to = "SOCIDE", values_to = "MEAN") %>%
  pivot_longer(c(SD_SAMERACE_MAJOR, SD_SAMERACE_MINOR, SD_SAMERACE), names_to = "SOCIDE_M", values_to = "SD") %>%
  ggplot(aes(x=TRIAL, y=MEAN, color=SOCIDE)) + 
  geom_line(stat="identity", size=1) +
  geom_ribbon(aes(ymin = (MEAN-SD), ymax = (MEAN + SD), fill  = "SOCIDE"), linetype = 0, alpha = 0.09, show.legend = F) +
  facet_grid(TIEOUT ~ TIECAP,
    labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "top") +
    labs(title = "Ego-Alter Similarity", 
    x = "-th Simulation", y = "Mean Percent (of all alters)", color = "Social Identity") +
  scale_color_manual(name= "", #"Ethnic", 
                  labels = c("all", "majority", "minority"), 
                    values = c("red", "#ED8E7C", "#A03C78")) +
    scale_fill_manual(values = c("red", "#ED8E7C", "#A03C78")) +
    scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) + ylim(0,100)

```

# AGENT SATISFACTION

## tab

percent

```{r}

agent_satis <- tibble(ID=agent_population$ID)
agent_satis$SATISFIED <- NA

agent_satis$SATISFIED <- sapply(1:nrow(agent_satis), function(i) who_satisfied(agent_population$POPULATION[[i]], agent_friendship$FRIENDSHIP[[i]]$results)$percentage[[1]] )

```

summary table for agent satisfaction

```{r, warning = F, message=F, echo=FALSE}

summ_agent_satisfied <- left_join(agent_satis, agent_population[,2:4], by="ID") %>%
  group_by(TIEOUT, TIECAP) %>%
  summarize(MEAN_SATISFIED = round(mean(SATISFIED),2), SD_SATISFIED = round(sd(SATISFIED),2))

summ_agent_satisfied

```

## viz

percent (for manuscript)

```{r}

satisfied_agent_df <- left_join(agent_population[,1:4], agent_satis, by="ID")
satisfied_agent_df$UNSATISFIED<- 100-agent_satis$SATISFIED

satisfied_agents_plot <- satisfied_agent_df %>%
  pivot_longer(SATISFIED:UNSATISFIED, names_to = "Satisfaction", values_to = "Count") %>%
  ggplot(aes(x=TRIAL, y=Count, fill=Satisfaction)) +
  geom_area() + 
  facet_grid(TIEOUT ~ TIECAP,
             labeller = labeller(TIECAP = p_tc_labs, TIEOUT = p_to_labs)) + 
  labs(title = "Agent Satisfaction", 
    x = "-th Simulation", y = "Percent (of all agents)") + scale_x_continuous(breaks = c(1, 25, 50, 75, 100)) +
  scale_fill_manual(name="", labels = c("satisfied agents", "unsatisfied agents"), values = c("#b6c867", "01937c")) + 
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "top")

satisfied_agents_plot

```

